Geometric variational problems

### 2020-11-14 NSF2020/Description/specificaim1_ver2.tex
fixed typos in SA 1; made up title for our work in progress

\section{Proposed Research}
\label{sec:proposed-work}
%The proposed research develops fast,
%high-order-accurate, parallel numerical algorithms for large-scale
%simulations of the collective hydrodynamics of amphiphilic particles in a viscous solvent.
%%
We have demonstrated that our hydrophobic attraction with repulsion
potential (HAP) approach efficiently simulates self-assembly of
amphiphilic particles into two-dimensional micelles, bilayer membranes,
and vesicles \cite{Fu2018_SIAM}, and recreates the tank-treading
phenomenon in external shear flows \cite{Fu20} \todo{Is this supposed
to be a reference to our working paper}.
%\todo[inline]{!!let's put a proceedings here so we have something to cite!!}.
%
While the results show great promise in the field of collective body
hydrodynamics, several outstanding issues need to be addressed. These
include a thorough analysis of elastic properties of our coarse-grained
bilayers, and efficiently simulating three-dimensional collective
hydrodynamics of amphiphilic particles.
Finally, we must incorporate electric charge and account
for how external fields control for particle self-assembly. 
%mathematically
%characterize the variational behavior of HARP under appropriate
%homogenized limits.

\subsection{Specific Aim 1: Measuring material properties of self-assembly of amphiphiles}
\label{subsec:specific_aim_1}

%\begin{figure}
%\begin{center}
%\includegraphics[width=0.9\textwidth]{figures/SA1_fig1.pdf}
%\end{center}
%\caption{\footnotesize (A--C) The splay ($\Div \mathbf{d}$), 
%saddle splay ($\det \mathsf{D}$) and twist ($\Curl \mathbf{d}$) elastic distortions of 
%a monolayer. (D) The monolayer neutral surface $\Sigma$,  
%director $\mathbf{d}$ and unit normal $\mathbf{n}$ in local coordinates.
%(E--F) Lipids are able to tilt from  the surface normal, and stretch.
%(H--J) Intermediates of membrane fusion and (K) experimental image of a stalk \cite{Aeffner2012}. }
%\label{fig:distortions}
%\end{figure}
The goal of Specific Aim 1 is to characterize the material properties of many-body, self-assembled amphiphiles.
For amphiphiles assembled into bilayers, these properties are described by membrane continuum mechanics.
Our goal is to be able to map the parameters of the particle-based model onto the elastic moduli from continuum theory.
Results from this goal will facilitate simulators to use the hydrophobic attraction force calculations
to model bilayers with specific composition. These calculations have provably less computational complexity than
those of molecular dynamics simulations and possess the molecular granularity lacking from continuum models.

Hamm and Kozlov (HK) pioneered 
the modern theory of membrane continuum mechanics \cite{Hamm2000}, and their theory
%was pioneered by Hamm and Kozlov (HK) \cite{Hamm2000}. The theory 
is widely used to describe biological phenomena 
fission \cite{FrEsAkSh15, Maetal15, PhysRevE.79.031926},
fusion \cite{ChKo08, KoKo2002,Kuzmin7235,Aeffner2012},
poration \cite{Gaetal20}, phase boundaries, and interaction with inclusions
\cite{SeLeMaEg17,Saetal20, Pietal20}. These phenomena
require resolution of the internal structure of the membrane.  
Recently, there has been a revival in interest in the HK theory as the quadratic assumption
for the elasticity energy density has caused
researchers to question the applicability of the theory 
for large curvatures
\cite{PhysRevLett.117.188102, ARGUDO20161619}.
%
\begin{wrapfigure}[11]{l}{0.47\textwidth}
\centerline{\includegraphics[width=0.47\textwidth]{Figures/Deformations.pdf}}
%  \centering{\includegraphics[width=0.80\textwidth]{Figures/Deformations.pdf}}
  \vspace{-5pt}
\caption{\label{fig:deformations} \footnotesize Sketch of the HK
 membrane model \cite{Hamm2000}.}
\end{wrapfigure}
%
This proposal will develop much-needed mathematical analysis to resolve
these controversies due to the assumptions in the HK theory. 
%Using the HK  model as a base,
%PI RR and collaborators calculated, for the first time in continuum theory, a least energy path for transitions between planar bilayers, a membrane stalk,
%hemifusion diaphragm and the fusion pore \cite{RyWaCo13,RyKlYaCo16},
%and the energies calculated by these continuum studies (Figure \ref{fig:barriers}A),
%are in agreement with barrier heights derived by molecular dynamics and experimental studies \cite{FrRoPi17}.

@@

The HK framework assumes a three-dimensional lipid monolayer with internal structure
consisting of straight fibers that represent elongated hydrocarbon chains.
The framework assumes an elastic energy density ${\cal W}$ that is quadratic in the
Green-Lagrange strain tensor for membrane deformation of
this striated, internal structure.
%
%
%
%These fibers
%tilt and stretch with respect to the dividing surface--the surface formed lying between the hydrocarbon chains and polar heads of lipids.
%Accordingly, the deformation takes the form 
%\begin{equation}
%  \label{LMdeformation}
%{\bf x}(X_1, X_2, X_3) = {\bf x}_0(X_1, X_2) + \zeta(x_0(X_1, X_2), X_3) {\bf n}(x_0(X_1, X_2))
%\end{equation}
%where $(X_1,X_2,X_3)$ are points in a reference volume.
%The map $x_0$ parametrizes the dividing surface $\Sigma$, and the unit vector field ${\bf n}$ parametrizes the
%direction of the lipid tails in the deformed state \cite{doi:10.1021/jp075641w,KLAUDA20083074}.
%The parameter $X_3$ and the function $\zeta$ parametrizes the distance along the hydrocarbon chain in the reference state
%and the deformed state, respectively, and so $0 \leq X_3 \leq \delta$ where $\delta = $ 2.5 nm is a realistic monolayer thickness. 
%
%The elastic theory assumes an energy density that is quadratic in the Green-Lagrange strain tensor for ${\bf x}$. 
%The chains stretch and compress to satisfy incompressibility.
%Symmetries with respect to mirror reflection and in-plane rotation, the internal structure assumptions and incompressibility
%lead to an elastic surface energy over the dividing surface $\Sigma$. 
%
This energy density decomposes into four, fundamental, and independent
deformations (Figure~\ref{fig:deformations}): splay ($\Div {\bf n}$),
twist ($\Curl {\bf n}$), saddle splay ($\det \nabla {\bf n}$), and tilt
${\bf t}={\bf n}/({\bf N}\cdot {\bf n}) - {\bf N}$ where ${\bf N}$ is
the unit surface normal:
\begin{equation}
\label{ansatz3}
{\cal W} \equiv \int_{\Sigma} 
  \tfrac{1}{2}\KB\left[ \left( \Div {\bf n} + k_0\right)^2 - k_0^2\right] 
+ \tfrac{1}{2}\KT (\Curl {\bf n})^2 + \KG  \det \nabla {\bf n} + \tfrac{1}{2}\KTH |{\bf t}|^2 \,dA.
\end{equation}
Here, 
%$(\nabla {\bf n})_{ij} = \partial_{x_j}{\bf n} \cdot {\bf e}_i$ is the surface gradient with
%orthonormal tangent vectors $\{{\bf e}_1, {\bf e}_2\}$.
%%\todo[inline]{YNY and BQ: What do you call a coordinate system where the metric is the identity at one point?}
%Also, the surface divergence 
%$\Div {\bf n}$ is the trace, and the surface curl $\Curl {\bf n}$ is the anti-trace (sum of the off-diagonal elements), of $\nabla {\bf n}$ respectively.
%respectively (Figure \ref{fig:distortions}A--C).
the deformations come with elastic coefficients: the bending modulus
$\KB$, twist modulus $\KT$, saddle-splay modulus $\KG$, and tilt modulus
$\KTH$.
%HK define the tilt vector ${\bf t} = {\bf n}/({\bf N}\cdot {\bf n}) - {\bf N}$ where ${\bf N}$ is the unit surface normal.
%
The parameter $k_0$ is the spontaneous curvature and determines the
preferred lipid splay~\cite{RoLi15,Kozlov2007}.  
%As an illustration, the
%lipid DSPC has $k_0 = -0.1$ nm$^{-1}$ 
%%as a result of  %having a relatively long acyl chain. 
%and these lipids would preferentially line the upper monolayer in Figure \ref{fig:deformations}B  
%because the addition of a positive splay 
%to the negative spontaneous curvature leads to lower energy \cite{Kamal22245, C3SM51829A, RoLi15,FriedSeguin15}.
%The subtraction of $k_0^2$ makes the energy distortion free
%\cite{Helfrich73,PhysRevLett.113.248102,Hamm2000}.

@@

%\begin{center}
%Anticipated model simulations
%\end{center}
\subsubsection{Simulations of the HARP model to estimate elastic moduli and energy}
%To characterize material properties of a bilayer, we compare the energies and forces generated by
%a collection of amphiphilic particles against the energies and forces of a continuum bilayer.
We propose to
%
%to examine conduct calculations similar to the example of figure~\ref{fig:flattening}
%for a wide range of particle parameters and physical parameters in HARP to 
%
%{\bf (i)} Assess whether the continuum energies \eqref{ansatz3} are the same
%as the corresponding energies in the particle system for all reasonable deformation.
%If this is the case we will 
%
{\bf (i)} determine the value of effective elastic moduli $\KB$,
$\KT$, $\KG$, and $\KTH$, and then {\bf (ii)} understand how the model parameters $\rho,$ $\gamma$, and
particle shape map onto elastic moduli. 
An accurate and robust way to measure material properties is to track the evolution of the bilayer as
%
\begin{wrapfigure}[10]{r}{0.4\textwidth}
\vspace{-0.3cm}
\centerline{\includegraphics[width=0.4\textwidth]{Figures/Flattening.pdf}}
%  \centering{\includegraphics[width=0.80\textwidth]{Figures/Deformations.pdf}}
\vspace{-0.2cm}
\caption{\label{fig:flattening} \footnotesize Example of computing
  bending modulus of a lipid bilayer from particle simulation.}
\end{wrapfigure}
it relaxes from an initially non-equilibrium
configuration~\cite{PhysRevLett.117.188102}. Figure~\ref{fig:flattening}
shows an example where the initial configuration of a lipid bilayer
patch contains only splay deformation without any other components
(saddle splay, twist and tilt). As the bent membrane flattens we find
that both the membrane self-interaction energy $\Phi$ and the elastic
energy ${\cal W}$ decrease, and because the saddle splay, twist, and
tilt stay zero, the slope gives the bending modulus in this case.

@@

Here we start with a particle-based bilayer in a specific non-equilibrium shape that involves only one of the components of the displacement in Figure~\ref{fig:deformations}, and then evolve the particle system according to the time integration for \eqref{eq:stokes}.
Actually,  elastic properties are independent of dissipation, and so we can forgo solving for fluid velocity and by setting the translational
velocity and angular velocity directly proportional to force and torque. 
%bilayer by steepest gradient descent 
%with respect to the HARP functional:
%\begin{equation}
%\label{SGD}   
%\frac{\dif {\bf a}_i}{\dif t} = {\bf F}_i,    \quad  \frac{\dif {\bf R}_i}{\dif t}  = {\bf R}_i A({\bf w}_i),\quad i = 1, \dots, N.
%\end{equation}
%where that particle centers ${\bf a}_i$ and rotation matrices ${\bf R}_i$ determine the particle configuraton; 
%$A({\bf w}_i)$ is the skew-symmetric matrix with axial vector ${\bf w}_i$.
%We solve \eqref{SGD} numerically  using an Adams–Bashforth linear multistep method. 
%The procedure involves solving \eqref{SL} based off of the current particle configuration.
%We then use the solution $u$ to calculate the collection of forces and torques \eqref{forceandtorque}, and update the particle configuration
%through \eqref{SGD}.

\begin{wrapfigure}[11]{l}{0.32\textwidth}
\centerline{\includegraphics[width=0.32\textwidth]{Figures/SaddleSplayDiagram.pdf}}
  \vspace{-8pt}
\caption{\label{fig:saddle_splay} \footnotesize Example of determining the
  saddle splay modulus.}
\end{wrapfigure}
%
This yields a dissipation of the total potential \eqref{eq:total_poten}, which
stabilizes the evolving bilayer shape.
Therefore, we reconstruct an evolving monolayer dividing surface $\Sigma$ and director field ${\bf n}$ by
interpolating the particle centers and orientations. Using \eqref{ansatz3}, we calculate a continuum energy $\mathcal{W}$ from the interpolated shapes.

@@

We propose to conduct calculations similar to the example of Figure~\ref{fig:flattening} for other elastic moduli such as the effective twist modulus $\KT$.
Molecular dynamics investigations find a twist modulus about 1
\kBT~\cite{LeVeWa14}, and here the specific non-equilibrium shape consists of
a single layer of amphiphilic particles on a hydrophobic substrate as
illustrated by Figure~\ref{fig:deformations}D. Having a nonzero twist
requires nonzero tilt (the surface gradient of the lipid
director equals the second fundamental form
%, and is therefore symmetric,
whenever tilt is zero locally). The twist deformation is a fully
three-dimensional deformation. \S\ref{subsec:specific_aim_3} addresses outstanding implementation issues like three-dimensional boundary integral equation solvers.

@@

%\subsubsection{HK elastic energy form}
\noindent{\bf{HK elastic energy form:}}
The field of membrane continuum mechanics still lacks consensus as to whether \eqref{ansatz3} is the appropriate functional for bilayer energy.
\textbf{(i)} Researchers have assumed that $\KT = 0$ because of the
relationship between twist the assumption of lateral fluidity in
membranes~\cite{Hamm2000, TerziDeserno17, C9SM02079A,
PhysRevE.102.042406}. 
A value $\KT = 0$, however, makes \eqref{ansatz3} a noncoercive functional.
%and leads to the nonphysical conclusion that there are bilayers 
%with $\nabla {\bf n} \to \infty$ but $\mathcal{W} \to 0.$ 
\textbf{(ii)} Recently,~\cite{TerziDeserno17} derived a tilt curvature
term that was neglected from the HK analysis~\cite{Hamm2000}.
Later,~\cite{C9SM02079A} and~\cite{PhysRevE.102.042406} independently
identified an inconsistency an the argument used
by~\cite{TerziDeserno17} arising
from a transversal tilt invariance assumption.
In~\cite{RyKlYaCo16}, PI RR and collaborators showed that the tilt vector leads to unphysical cusps depending on how one accounts for membrane thickness.  
\textbf{(iii)} Theoretical analysis of lipid phase transitions predict a
negative saddle-splay modulus around $-8$ \kBT~\cite{SIEGEL2004366,
SIEGEL20085200}, that gives rise to a larger energy barrier for
monolayer fusion than is found by experiments~\cite{FrRoPi17, Tran7106,
TerziDeserno17}.
%
%
%Researchers point out, however, that this theoretical value requires a larger energy 
%barrier for monolayer fusion than is found by experiment \cite{FrRoPi17,Tran7106,TerziDeserno17}.
%Furthermore, the stability conditions of \eqref{ansatz3} require $\KG \geq -4\min\{\KB,\KT\}$, suggesting a smaller magnitude for $\KG$.

@@

The form of the elastic energy density~\eqref{ansatz3} is the same as
the Oseen-Frank energy density for nematic liquid
crystals~\cite{ANDRIENKO2018520, Tran7106, Helfrich73}. In fact, a lipid
monolayer acts as one layer in a smectic phase~\cite{REYESMATEO1995978,
Rangamani20140463, PhysRevLett.113.248102}. Based on this observation,
we propose to examine the HK analysis to resolve the aforementioned
inconsistencies. We will expand the strain tensor in terms of a plane
perpendicular to ${\bf n}$ (instead of the monolayer tangent plane as
done in the past works) so that the gradient terms in the elastic energy
completely decouple. Using this expansion we prove an exact identity
that gives the incompressibility condition by a Steiner-type polynomial
in $\Div {\bf n}$ and $\det \nabla {\bf n}$ \cite{Fe59}. In contrast,
the works~\cite{TerziDeserno17, PhysRevE.102.042406, Hamm2000,
C9SM02079A} utilize an approximate identity for incompressibility, and
so we can offer a considerably more accurate analysis of monolayer
energy.

>>>>

\section{Proposed Research}
\label{sec:proposed-work}
%The proposed research develops fast,
%high-order-accurate, parallel numerical algorithms for large-scale
%simulations of the collective hydrodynamics of amphiphilic particles in a viscous solvent.
%%
We have demonstrated that our hydrophobic attraction with repulsion
potential (HAP) approach efficiently simulates self-assembly of
amphiphilic particles into two-dimensional micelles, bilayer membranes,
and vesicles \cite{Fu2018_SIAM} and recreates the tank-treading
phenomenon in external shear flows \cite{FuQuRyYo20}.
While the results show great promise in the field of collective body
hydrodynamics, several outstanding issues need to be addressed. These
include a thorough analysis of elastic properties of our coarse-grained
bilayers and efficiently simulating three-dimensional collective
hydrodynamics of amphiphilic particles.
We must also incorporate electric charge and account
for how external fields control particle self-assembly. 
%mathematically
%characterize the variational behavior of HARP under appropriate
%homogenized limits.

\subsection{Specific Aim 1: Measuring material properties of amphiphile self-assembly}
\label{subsec:specific_aim_1}

%\begin{figure}
%\begin{center}
%\includegraphics[width=0.9\textwidth]{figures/SA1_fig1.pdf}
%\end{center}
%\caption{\footnotesize (A--C) The splay ($\Div \mathbf{d}$), 
%saddle splay ($\det \mathsf{D}$) and twist ($\Curl \mathbf{d}$) elastic distortions of 
%a monolayer. (D) The monolayer neutral surface $\Sigma$,  
%director $\mathbf{d}$ and unit normal $\mathbf{n}$ in local coordinates.
%(E--F) Lipids are able to tilt from  the surface normal, and stretch.
%(H--J) Intermediates of membrane fusion and (K) experimental image of a stalk \cite{Aeffner2012}. }
%\label{fig:distortions}
%\end{figure}
The goal of Specific Aim 1 is to characterize the material properties of many-body, self-assembled amphiphiles.
For amphiphiles assembled into bilayers, these properties are described by membrane continuum mechanics.
Our goal is to map the parameters of the particle-based model onto the elastic moduli from continuum theory.
Results from this goal will facilitate simulators to use the hydrophobic attraction force calculations
to model bilayers with specific composition. These calculations have provably less computational complexity than
those of molecular dynamics simulations and possess the molecular granularity lacking from continuum models.

Hamm and Kozlov (HK) pioneered 
the modern theory of membrane continuum mechanics \cite{Hamm2000}, and their theory
%was pioneered by Hamm and Kozlov (HK) \cite{Hamm2000}. The theory 
is widely used to describe biological phenomena, including 
fission \cite{FrEsAkSh15, Maetal15, PhysRevE.79.031926},
fusion \cite{ChKo08, KoKo2002,Kuzmin7235,Aeffner2012},
poration \cite{Gaetal20}, phase boundaries, and interaction with inclusions
\cite{SeLeMaEg17,Saetal20, Pietal20}. These phenomena
require resolution of the internal structure of the membrane.  
Recently, there has been a revival in interest in the HK theory as the quadratic assumption
for the elasticity energy density has caused
researchers to question the applicability of the theory 
for large curvatures
\cite{PhysRevLett.117.188102, ARGUDO20161619}.
%
\begin{wrapfigure}[11]{l}{0.47\textwidth}
\centerline{\includegraphics[width=0.47\textwidth]{Figures/Deformations.pdf}}
%  \centering{\includegraphics[width=0.80\textwidth]{Figures/Deformations.pdf}}
  \vspace{-5pt}
\caption{\label{fig:deformations} \footnotesize Sketch of the HK
 membrane model \cite{Hamm2000}.}
\end{wrapfigure}
%
This proposal will develop much-needed mathematical analysis to resolve
these controversies due to the assumptions in the HK theory. 
%Using the HK  model as a base,
%PI RR and collaborators calculated, for the first time in continuum theory, a least energy path for transitions between planar bilayers, a membrane stalk,
%hemifusion diaphragm and the fusion pore \cite{RyWaCo13,RyKlYaCo16},
%and the energies calculated by these continuum studies (Figure \ref{fig:barriers}A),
%are in agreement with barrier heights derived by molecular dynamics and experimental studies \cite{FrRoPi17}.

@@

The HK framework assumes a three-dimensional lipid monolayer where the internal structure
consists of straight fibers that represent elongated hydrocarbon chains.
The elastic energy density ${\cal W}$ is quadratic in the Green-Lagrange strain
tensor for this striated, internal structure.
%
%
%
%These fibers
%tilt and stretch with respect to the dividing surface--the surface formed lying between the hydrocarbon chains and polar heads of lipids.
%Accordingly, the deformation takes the form 
%\begin{equation}
%  \label{LMdeformation}
%{\bf x}(X_1, X_2, X_3) = {\bf x}_0(X_1, X_2) + \zeta(x_0(X_1, X_2), X_3) {\bf n}(x_0(X_1, X_2))
%\end{equation}
%where $(X_1,X_2,X_3)$ are points in a reference volume.
%The map $x_0$ parametrizes the dividing surface $\Sigma$, and the unit vector field ${\bf n}$ parametrizes the
%direction of the lipid tails in the deformed state \cite{doi:10.1021/jp075641w,KLAUDA20083074}.
%The parameter $X_3$ and the function $\zeta$ parametrizes the distance along the hydrocarbon chain in the reference state
%and the deformed state, respectively, and so $0 \leq X_3 \leq \delta$ where $\delta = $ 2.5 nm is a realistic monolayer thickness. 
%
%The elastic theory assumes an energy density that is quadratic in the Green-Lagrange strain tensor for ${\bf x}$. 
%The chains stretch and compress to satisfy incompressibility.
%Symmetries with respect to mirror reflection and in-plane rotation, the internal structure assumptions and incompressibility
%lead to an elastic surface energy over the dividing surface $\Sigma$. 
%
This energy density decomposes into four, fundamental, and independent
deformations (Figure~\ref{fig:deformations}): splay ($\Div {\bf n}$),
twist ($\Curl {\bf n}$), saddle splay ($\det \nabla {\bf n}$), and tilt
${\bf t}={\bf n}/({\bf N}\cdot {\bf n}) - {\bf N}$ where ${\bf N}$ is
the unit surface normal;
\begin{equation}
\label{ansatz3}
{\cal W} \equiv \int_{\Sigma} 
  \tfrac{1}{2}\KB\left[ \left( \Div {\bf n} + k_0\right)^2 - k_0^2\right] 
+ \tfrac{1}{2}\KT (\Curl {\bf n})^2 + \KG  \det \nabla {\bf n} + \tfrac{1}{2}\KTH |{\bf t}|^2 \,dA.
\end{equation}
Here, 
%$(\nabla {\bf n})_{ij} = \partial_{x_j}{\bf n} \cdot {\bf e}_i$ is the surface gradient with
%orthonormal tangent vectors $\{{\bf e}_1, {\bf e}_2\}$.
%%\todo[inline]{YNY and BQ: What do you call a coordinate system where the metric is the identity at one point?}
%Also, the surface divergence 
%$\Div {\bf n}$ is the trace, and the surface curl $\Curl {\bf n}$ is the anti-trace (sum of the off-diagonal elements), of $\nabla {\bf n}$ respectively.
%respectively (Figure \ref{fig:distortions}A--C).
the deformations come with elastic coefficients: the bending modulus
$\KB$, twist modulus $\KT$, saddle-splay modulus $\KG$, and tilt modulus
$\KTH$.
%HK define the tilt vector ${\bf t} = {\bf n}/({\bf N}\cdot {\bf n}) - {\bf N}$ where ${\bf N}$ is the unit surface normal.
%
The parameter $k_0$ is the spontaneous curvature and determines the
preferred lipid splay~\cite{RoLi15,Kozlov2007}.  
%As an illustration, the
%lipid DSPC has $k_0 = -0.1$ nm$^{-1}$ 
%%as a result of  %having a relatively long acyl chain. 
%and these lipids would preferentially line the upper monolayer in Figure \ref{fig:deformations}B  
%because the addition of a positive splay 
%to the negative spontaneous curvature leads to lower energy \cite{Kamal22245, C3SM51829A, RoLi15,FriedSeguin15}.
%The subtraction of $k_0^2$ makes the energy distortion free
%\cite{Helfrich73,PhysRevLett.113.248102,Hamm2000}.

@@

%\begin{center}
%Anticipated model simulations
%\end{center}
\subsubsection{Simulations of the HARP model to estimate elastic moduli and energy}
%To characterize material properties of a bilayer, we compare the energies and forces generated by
%a collection of amphiphilic particles against the energies and forces of a continuum bilayer.
We propose to
%
%to examine conduct calculations similar to the example of figure~\ref{fig:flattening}
%for a wide range of particle parameters and physical parameters in HARP to 
%
%{\bf (i)} Assess whether the continuum energies \eqref{ansatz3} are the same
%as the corresponding energies in the particle system for all reasonable deformation.
%If this is the case we will 
%
{\bf (i)} determine the value of effective elastic moduli $\KB$,
$\KT$, $\KG$, and $\KTH$ and then {\bf (ii)} understand how the model parameters $\rho,$ $\gamma$, and
particle shape map onto elastic moduli. 
An accurate and robust way to measure material properties is to track the evolution of the bilayer as
%
\begin{wrapfigure}[10]{r}{0.4\textwidth}
\vspace{-0.3cm}
\centerline{\includegraphics[width=0.4\textwidth]{Figures/Flattening.pdf}}
%  \centering{\includegraphics[width=0.80\textwidth]{Figures/Deformations.pdf}}
\vspace{-0.2cm}
\caption{\label{fig:flattening} \footnotesize Example of computing
  bending modulus of a lipid bilayer from particle simulation.}
\end{wrapfigure}
it relaxes from an initially non-equilibrium
configuration~\cite{PhysRevLett.117.188102}. Figure~\ref{fig:flattening}
shows an example where the initial configuration of a lipid bilayer
patch contains only splay deformation without any other components
(saddle splay, twist and tilt). As the bent membrane flattens, we find
that both the membrane self-interaction energy $\Phi$ and the elastic
energy ${\cal W}$ decrease, and because the saddle splay, twist, and
tilt stay zero, the slope gives the bending modulus in this case.

@@

Here we start with a particle-based bilayer in a specific non-equilibrium shape that involves only one of the components of the displacement in Figure~\ref{fig:deformations}, and then evolve the particle system according to the time integration for \eqref{eq:stokes}.
Because elastic properties are independent of dissipation,
we can forgo solving for fluid velocity and set the translational
velocity and angular velocity directly proportional to force and torque. 
%bilayer by steepest gradient descent 
%with respect to the HARP functional:
%\begin{equation}
%\label{SGD}   
%\frac{\dif {\bf a}_i}{\dif t} = {\bf F}_i,    \quad  \frac{\dif {\bf R}_i}{\dif t}  = {\bf R}_i A({\bf w}_i),\quad i = 1, \dots, N.
%\end{equation}
%where that particle centers ${\bf a}_i$ and rotation matrices ${\bf R}_i$ determine the particle configuraton; %
%$A({\bf w}_i)$ is the skew-symmetric matrix with axial vector ${\bf w}_i$.
%We solve \eqref{SGD} numerically  using an Adams–Bashforth linear multistep method. 
%The procedure involves solving \eqref{SL} based off of the current particle configuration.
%We then use the solution $u$ to calculate the collection of forces and torques \eqref{forceandtorque}, and update the particle configuration
%through \eqref{SGD}.
%
\begin{wrapfigure}[11]{l}{0.32\textwidth}
\centerline{\includegraphics[width=0.32\textwidth]{Figures/SaddleSplayDiagram.pdf}}
  \vspace{-8pt}
\caption{\label{fig:saddle_splay} \footnotesize Example of determining the
  saddle splay modulus.}
\end{wrapfigure}
%
This yields a dissipation of the total potential \eqref{eq:total_poten}, which
stabilizes the evolving bilayer shape.
Therefore, we reconstruct an evolving monolayer dividing surface $\Sigma$ and director field ${\bf n}$ by
interpolating the particle centers and orientations. Using \eqref{ansatz3}, we calculate a continuum energy $\mathcal{W}$ from the interpolated shapes.

@@

We propose to conduct calculations similar to the example of Figure~\ref{fig:flattening}
for other elastic moduli such as the effective twist modulus $\KT$.
Molecular dynamics investigations find a twist modulus about 1
\kBT~\cite{LeVeWa14}, and here, the specific non-equilibrium shape consists of
a single layer of amphiphilic particles on a hydrophobic substrate as
illustrated by Figure~\ref{fig:deformations}D. Having a nonzero twist
requires nonzero tilt because the surface gradient of the lipid
director equals the second fundamental form
%, and is therefore symmetric,
whenever tilt is zero locally. The twist deformation is a fully
three-dimensional deformation. \S\ref{subsec:specific_aim_3} addresses outstanding implementation issues like three-dimensional boundary integral equation solvers.

@@

%\subsubsection{HK elastic energy form}
\noindent{\bf{HK elastic energy form:}}
The field of membrane continuum mechanics still lacks consensus as to whether \eqref{ansatz3} is the appropriate functional for bilayer energy.
\textbf{(i)} Researchers have assumed that $\KT = 0$ to effect lateral fluidity in
membranes~\cite{Hamm2000, TerziDeserno17, C9SM02079A,
PhysRevE.102.042406}. 
A value $\KT = 0$, however, makes \eqref{ansatz3} a noncoercive functional.
%and leads to the nonphysical conclusion that there are bilayers 
%with $\nabla {\bf n} \to \infty$ but $\mathcal{W} \to 0.$ 
\textbf{(ii)} Recently,~\cite{TerziDeserno17} derived a tilt curvature
term that was neglected from the HK analysis~\cite{Hamm2000}.
Later,~\cite{C9SM02079A} and~\cite{PhysRevE.102.042406} independently
identified an inconsistency in the argument used
by~\cite{TerziDeserno17} arising
from a transversal tilt invariance assumption.
In~\cite{RyKlYaCo16}, PI RR and collaborators showed that the tilt vector leads to unphysical cusps depending on how one accounts for membrane thickness.  
\textbf{(iii)} Theoretical analysis of lipid phase transitions predict a
negative saddle-splay modulus around $-8$ \kBT~\cite{SIEGEL2004366,
SIEGEL20085200} that gives rise to a larger energy barrier for
monolayer fusion than is found by experiments~\cite{FrRoPi17, Tran7106,
TerziDeserno17}.
%
%
%Researchers point out, however, that this theoretical value requires a larger energy 
%barrier for monolayer fusion than is found by experiment \cite{FrRoPi17,Tran7106,TerziDeserno17}.
%Furthermore, the stability conditions of \eqref{ansatz3} require $\KG \geq -4\min\{\KB,\KT\}$, suggesting a smaller magnitude for $\KG$.

@@

The form of the elastic energy density~\eqref{ansatz3} is the same as
the Oseen-Frank energy density for nematic liquid
crystals~\cite{ANDRIENKO2018520, Tran7106, Helfrich73}. In fact, a lipid
monolayer acts as one layer in a smectic phase~\cite{REYESMATEO1995978,
Rangamani20140463, PhysRevLett.113.248102}. Based on this observation,
we propose to examine the HK analysis to resolve the aforementioned
inconsistencies. We will expand the strain tensor in terms of a plane
perpendicular to ${\bf n}$ (instead of the monolayer tangent plane as
done in the past works) so that the gradient terms in the elastic energy
completely decouple. Using this expansion we prove an exact identity
that gives the incompressibility condition by a Steiner-type polynomial
in $\Div {\bf n}$ and $\det \nabla {\bf n}$ \cite{Fe59}. In contrast,
the works~\cite{TerziDeserno17, PhysRevE.102.042406, Hamm2000,
C9SM02079A} utilize an approximate identity for incompressibility as a base,
so we can considerably improve upon the analysis of monolayer energy.
